Titulo

### 2015-02-11 RotacionOutFlows/Paper/ms.tex
minor changes

In 1967 \cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Ostlin14}  ,  become a very important tool to 
explore the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
line is redshifted into the optical regime. it is specially useful to study the 
properties of the high redshift Universe, such as the large scale structure.
and new projects are beeing planned for the near future $\cite{}$.

@@

To fully understand the observed spectra of LAEs this galaxies must be modeled.
however the resonant nature of the lines makea this a challenging task. 
\cite{Neufeld90} the outcoming spectra of galaxies through static mediums 
Recent hydrodynamical simulations have been explored the properties of the IGM/ISM 
in large scale simulations, while some others have studied detailed galaxies. 
On the other hand RT computations have been in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.

>>>>

\cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Ostlin14} with the aim of  
exploring the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
line is redshifted into the optical regime. With the outcoming of new and powerfull telescopes
such as the James Webb Space Telescope new LAEs are going to be discovered.

@@

To fully understand the observed spectra of LAEs this galaxies must be modeled.
However the resonant nature of the lines makes this a challenging task. 
Analytical solutions for the outcoming spectra in simple ISM static geometries have been dereived
\cite{Neufeld90}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
in large scale simulations, while some others have studied detailed galaxies. 
Radiative transfer codes have been used in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.
